---
title: "Examining Factors Contributing to Attrition"
author: "Lakshmi Bobbillapati, Stanford Finney, Laura Ludwig, Ryan Talk"
date: "November 25, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(xlsx)
library(mlbench)
library(caret)
library(vcd)
library(ICC)
library(corrplot)
library(knitr)
library(Hmisc)
library(corrplot)

```

## Introduction

This analysis explores a data set regarding attrition (an employee voluntarily leaving a company). The goal is to identify what characteristics of an employee are good indicators that an employee is at risk of leaving. 

## Data Exploration

```{r gather}
dat <- read.csv("CaseStudy2-data.csv")
head(dat)
summary(dat)
```

From this summary, there are 35 variables, and 1470 observations. The variable of interest is "Attrition", which is a binary "Yes/No" outcome. A number of the variables are redundant or non-informative: "Over18", "StandardHours" and "EmployeeCount" have only one value each; "EmployeeNumber" is an ID. 

```{r clean}
dat <- subset(dat, select = -c(Over18,EmployeeCount,StandardHours)) #Remove the columns that do not give any useful information.
dat$Att <- ifelse(dat$Attrition == "Yes", 1,0) #Create a numeric representation of Attrition (1=Yes, 0=No)

```

To start exploring the data, look at boxplots/histograms based on Attrition. 
This would be a good place for us to examine our transformations
```{r boxplots}
# Maybe include some relevant box plots
```

## Evaluating Correlations between Variables

### Categorical Variables



```{r corr_cat}

#Create a function to look at Kramer correlations between categorical variables
catcorrm <- function(vars, dat) sapply(vars, function(y) sapply(vars, function(x) assocstats(table(dat[,x], dat[,y]))$cramer))
#Create a vector of the names of the categorical variables from the data set
catvars <- c("Attrition","BusinessTravel","Department","EducationField","Gender","JobRole","MaritalStatus","OverTime","EnvironmentSatisfaction","JobInvolvement","JobLevel","JobSatisfaction","PerformanceRating","RelationshipSatisfaction","StockOptionLevel","WorkLifeBalance","NumCompaniesWorked")
#Run the Kramer correlation function
mat <- catcorrm(vars=catvars,dat)
kable(mat)

corrplot(mat, type="upper", tl.cex=0.5, tl.col="black")
```

### Continuous Variables
```{r corr_cont}
cont <- subset(dat, select=c(Att, Age,DailyRate,DistanceFromHome,HourlyRate,MonthlyIncome,MonthlyRate,NumCompaniesWorked,PercentSalaryHike,TotalWorkingYears,TrainingTimesLastYear,YearsAtCompany,YearsInCurrentRole,YearsSinceLastPromotion,YearsWithCurrManager))
#Run correlation matrix
res <- rcorr(as.matrix(cont))
#Plot the correlations to see which ones are highly important
kable(res$r)
corrplot(res$r,type="upper",p.mat=res$P, sig.level=0.1, insig="blank", tl.cex=0.5,tl.col="black")
# Variables related to years are all significantly correlated (TotalWorkingYears,YearsAtCompany,YearsInCurrentRole,YearsSinceLastPromotion,YearsWithCurrManager).
# Age is significantly correlated with TotalWorkingYears and MonthlyIncome.
# MonthlyIncome is significantly correlated with the variables related to years (see above comment for list).
# By adding Att to this, it's possible to see which continous variables are correlated to Attrition


```
```{r corr_cont}
#Add details here around evaluating the continuous variable correlations

```

Make sure to add some description about which variables have the highest correlations.

## Trends by Job Role
Details about the process and outcomes of Lakshmi's analysis on Job Roles.
```{r jobrolesbyattrition}

```
[How to read this plot type]
Interesting observation 1


```{r jobrolesbygender}

```

```{r jobrolesbyx}

```
## Conclusion
Here we will need to tie together the results from our analysis.


