---
title: "Examining Factors Contributing to Attrition"
author: "Lakshmi Bobbillapati, Stanford Finney, Laura Ludwig, Ryan Talk"
date: "November 25, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(xlsx)
library(mlbench)
library(caret)
library(vcd)
library(ICC)
library(corrplot)
library(knitr)
```

## Introduction

This is where we will write an introduction to the problem and analysis we are completing.

## Data Exploration

```{r gather}
dat <- read.xlsx("CaseStudy2-data.xlsx", sheetName="HR-employee-attrition Data")
head(dat)
summary(dat)
```

From this summary, there are 35 variables, and 1470 observations. The variable of interest is "Attrition", which is a binary "Yes/No" outcome. A number of the variables are redundant or non-informative: "Over18", "StandardHours" and "EmployeeCount" have only one value each; "EmployeeNumber" is an ID. 

```{r clean}
dat <- subset(dat, select = -c(Over18,EmployeeCount,StandardHours)) #Remove the columns that do not give any useful information.
dat$Att <- ifelse(dat$Attrition == "Yes", 1,0) #Create a numeric representation of Attrition (1=Yes, 0=No)

```

To start exploring the data, look at boxplots/histograms based on Attrition. 
This would be a good place for us to examine our transformations
```{r boxplots}
# Maybe include some relevant box plots
```

## Evaluating Correlations between Variables

```{r corr_cat}

#Create a function to look at Kramer correlations between categorical variables
catcorrm <- function(vars, dat) sapply(vars, function(y) sapply(vars, function(x) assocstats(table(dat[,x], dat[,y]))$cramer))
#Create a vector of the names of the categorical variables from the data set
catvars <- c("Attrition","BusinessTravel","Department","EducationField","Gender","JobRole","MaritalStatus","OverTime","EnvironmentSatisfaction","JobInvolvement","JobLevel","JobSatisfaction","PerformanceRating","RelationshipSatisfaction","StockOptionLevel","WorkLifeBalance","NumCompaniesWorked")
#Run the Kramer correlation function
mat <- catcorrm(vars=catvars,dat)
kable(mat)
```
```{r corr_cont}
#Add details here around evaluating the continuous variable correlations
```

Make sure to add some description about which variables have the highest correlations.

## Trends by Job Role
Details about the process and outcomes of Lakshmi's analysis on Job Roles.
```{r jobroles}

```

## Conclusion
Here we will need to tie together the results from our analysis.


