---
title: "Data Science Case Study 2"
author: "Lakshmi Bobbillapati, Stanford Finney, Laura Ludwig, Ryan Talk"
date: "November 25, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(xlsx)
library(mlbench)
library(caret)
```

## Introduction

This is where we will write an introduction to the problem and analysis we are completing.

## Data Exploration

```{r gather}
dat <- read.xlsx("CaseStudy2-data.xlsx", sheetName="HR-employee-attrition Data")
head(dat)
summary(dat)
```

From this summary, there are 35 variables, and 1470 observations. The variable of interest is "Attrition", which is a binary "Yes/No" outcome. A number of the variables are redundant or non-informative: "Over18" and "EmployeeCount" have only one value each; "EmployeeNumber" is an ID. 

```{r clean}
dat <- subset(dat, select = -c(Over18,EmployeeCount)) #Remove the columns that do not give any useful information.
dat$Att <- ifelse(dat$Attrition == "Yes", 1,0) #Create a numeric representation of Attrition (1=Yes, 0=No)

# Create variable for age group
attach(dat)
dat$AgeGroup[Age <= 24] <- "18-24"
dat$AgeGroup[Age > 24 & Age <=34] <- "25-34"
dat$AgeGroup[Age > 34 & Age <=44] <- "35-44"
dat$AgeGroup[Age > 44 & Age <=54] <- "45-54"
dat$AgeGroup[Age > 54 & Age <=64] <- "55-64"
dat$AgeGroup[Age >= 65] <- "65+"
detach(dat)
```

```{r vet}
## CODE

```

## Conclusion
Here we will need to tie together the results from our analysis.


